---
title: "Survey project"
author: "Hasnaâ LATIQUE; Appanna"
date: "1/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

About the Project / the survey
The aim of our survey is to study whether or not Covid_19 has an impact on our daily lives

Our target population: we shared it in groups of students and employees
Sentimental analysis towards covid_19


# Questions
The Information we want to collect: 
- Does the covid_19 have an impact on people's psychology, for instance Is there a relationship between covid_19 and stress, loneliness or any other negative feelings?
- Is it responsible for some behavioral changes?
- Does it have a relationship with jobs offers and internships?

To do that, we are going to perform both univariate and bivariate descriptive analysis

```{r}
library(data.table)
library(reshape2)
library(tidyverse)
library(ggplot2)
library(pander)
```


#1.Import dataset
#list the name of each variable (data column) and the first six rows of the dataset
After uploading our data, we look at an overview of a part of it to check that it was correctly imported.
Below is a glimpse at what the data frame looks like
```{r}

#results <- read.csv2("results-survey-Covid.csv", sep=";")
results_data <- fread("results-survey-Covid.csv")
class(results_data)
```

```{r}
head(results_data)
```


#2.data preprocessing
Remove the white spaces and special characters in the columns names
```{r}
names(results_data)<-str_replace_all(names(results_data), c(" " = ".", "\\s" = ".", "-"=".", "'"=".",'\\['=".",'\\]'=".", "\\?"="."))
names(results_data)
```

```{r}
names(results_data)[28] <- 'Stress.comments'  #duplicate column name changed
names(results_data)
```

Rename columns
```{r}
results_data<-results_data %>% rename(Age=  How.old.are.you.,
    Gender= What.is.your.ge..,
    Livinginfo= Are.you.staying..,
    Familyin = If.you.re.livin..,
    Familyout = is.it.within.th..,
    Friends = How.often.do.yo..,
    Sadness = What.do.you.thi.....Sad.,
    Stressfree = What.do.you.thi.....Normal.,
    Frustration = What.do.you.thi.....Frustrated.,
    Worry= What.do.you.thi.....Worried.,
    Other.feeling= What.do.you.thi.....Other.,
    Loneliness.rate = On.a.scale.of.0..,
    Stress.rate= Are.you.stresse..,
    Level.studies = If.you.re.a.stu..,
    Internship = If.you.were.loo..,
    Renumeration=is.it.,
    Job= Has.COVID.19.im..,
    Productivity = How.impactful.t..,
    Productivity.comments = How.impactful.t.....Comment.,
    Use.screen= What.changes.ha.....Use.of.screens.,
    Physical.activity = What.changes.ha.....Physical.activity., 
    Hours.sleep = What.changes.ha.....Hours.of.sleep.,
    Stressful.things=Are.you.stresse..,
    Other.comments = Do.you.have.any..,
    Future.Contact=Can.we.contact...)
```

```{r}
names(results_data)
```

Remove irrelevant columns
```{r}
results_data1<-subset(results_data,select=-c(Response.ID,Date.submitted,Last.page,Start.language, Seed ))
summary(results_data1)
```
#Verify the type of each variable
```{r}
str(results_data1)
```
#Convert categorical columns to factors
```{r}
results_data2 <- as.data.frame(unclass(results_data1)) #read categorical columns as factors
str(results_data2)

```

 
 # observations
All of our variables are qualitative

1.There are 23 variables in the dataset ( The target variable: Emotions and patterns changes due to Covid)

2.All of our variables are qualitative




#3.data analysis
Now let's plot some graphs to gain better insights about our data-set and understand the existing patterns.
#Univariate analyses
we start with a uniform analysis of the variable age

#Number of observations and frequencies
```{r}
for (names in colnames(results_data2)) {
  print(names)
  t <-table(results_data2[,names])
  print(t)
  print(round(prop.table(t)*100,2))
}
```

#Bar chart (Not working)
```{r}
par (mfrow=c(1,1))
for (names in colnames(results_data2)){
  plot(results_data2[,names ], col="lightgreen", ylab = "Effectif", main=paste(names))
}
```


#Pie chart
```{r}
for(names in colnames(results_data2)){
  pie(table(results_data2[,names]),
      col=c("chocolate", "chocolate4", "chocolate1", "chocolate2", "chocolate3"), main=paste(names))
}
par(mfrow = c(1,1))
```




```{r}
ggplot(results_data2, aes(x = Gender)) + 
  geom_bar(fill = "blue", 
           colour="black") +
  labs(x = "Gender", 
       y = "Frequency", 
       title = " Target gender")
```
The variable productivity
```{r}
ggplot(results_data2, aes(x = Productivity)) +
  geom_bar()
```




#Bivariate analyses
#between two qualitative variables

```{r}
str(results_data2)
```


#Define categories of data
```{r}
personal_stats<-c('Age','Gender','Livinginfo','Familyin','Familyout','Friends')
symptoms<-c('Sadness','Stressfree','Frustration','Worry','Loneliness.rate', 'Stressful.things')
professional_stats<-c('Level.studies','Internship','Renumeration','Job')
habits<-c('Productivity','Use.screen','Physical.activity','Hours.sleep')
comments<-c('Other.feeling','Productivity.comments','Stress.comments','Other.comments')

```

#Contingency tables
## personal stats vs symptoms
```{r}
for (cat in personal_stats){
  for (name in symptoms){
    t<-table(results_data2[,cat],results_data2[,name])
    print(paste0(cat,' vs ',name))
    print(t)
  }
}
```

```{r}
# In percentage of total number of observations
t <- table(Read=results_data2$Friends,Loneliness=results_data2$Loneliness.rate)
#round(prop.table(t)*100,2)
# Just values

## Percentage of column total
t <- cbind(t, Total = rowSums(t))
round(prop.table(t,2),2)

## In percentage of line total
#t <- rbind(t, Total = colSums(t))
#round(prop.table(t,1),2)

```

## professional stats vs symptoms
```{r}
for (cat in professional_stats){
  for (name in symptoms){
    t<-table(results_data2[,cat],results_data2[,name])
    print(paste0(cat,' vs ',name))
    print(t)
  }
}
```


## personal_stats vs habits
```{r}
for (cat in personal_stats){
  for (name in habits){
    t<-table(results_data2[,cat],results_data2[,name])
    print(paste0(cat,' vs ',name))
    print(t)
  }
}
```

## professional stats vs habits
```{r}
for (cat in professional_stats){
  for (name in habits){
    t<-table(results_data2[,cat],results_data2[,name])
    print(paste0(cat,' vs ',name))
    print(t)
  }
}
```
## personal stats vs comments
```{r}
for (cat in personal_stats){
  for (name in comments){
    t<-table(results_data2[,cat],results_data2[,name])
    print(paste0(cat,' vs ',name))
    print(t)
  }
}
```
## proffesional stats vs comments
```{r}
for (cat in professional_stats){
  for (name in habits){
    t<-table(results_data2[,cat],results_data2[,name])
    print(paste0(cat,' vs ',name))
    print(t)
  }
}
```


```{r}
ggplot(results_data2, 
       aes(x = Age, 
           fill = Gender)) + 
  geom_bar(position = "stack")
```

```{r}
results_data2 %>%
    group_by(Worry,Job) %>%
    summarize(frequency = n()) %>%
    pander
```

What we can conclude from this is that job loss did not influence on the degree of worry

```{r}
results_data2 %>%
    group_by(Worry,Livinginfo) %>%
    summarize(frequency = n()) %>%
    pander
```


```{r}
results_data2 %>%
    group_by(Stressful.things,Job) %>%
    summarize(frequency = n()) %>%
    pander
```


```{r}
results_data %>%
    group_by(Stressful.things,Livinginfo) %>%
    summarize(frequency = n()) %>%
    pander
```





